%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,letterpaper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

\newcommand\cpp{C\raisebox{0.5ex}{\tiny\textbf{++}}}

 \renewcommand*{\labelitemi}{\strut\textcolor{color1}{\large\rmfamily\textbullet}}
% adjust the page margins
\usepackage[top=.1in, bottom=.1in, left=.6in, right=.6in]{geometry}

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Michael}{Bales}
%\address{726 De La Vina}{Santa Barbara Ca 93101}{}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[fixed]{(941) 660-3380}
\email{mtbales@fastmail.fm}                               % optional, remove / comment the line if not wanted
\homepage{www.mtbales.com}                         % optional, remove / comment the line if not wanted
\social[github]{http://github.com/slapplebags}                              % optional, remove / comment the line if not wanted

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\vspace{-1mm}
\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
\section{Experience}
\cventry{2018 -- Present}{IT Support Specialist}{LogMeIn}{Goleta, CA}{}{
  \begin{itemize}
    \item Windows, Mac, and Linux user support expert covering all aspects of end user needs for 800+ employees across the West coast, Central US, Puerto Rico, Guatemala, and Brazil
    \item Implemented internal documentation system centralizing the world wide IT documentation and support materials
    \item Worked with the Cisco networking team to complete the roll out of a new VPN system
  \end{itemize}
}

\cventry{2017 -- 2018}{Network Engineer}{Latitude 34 Technologies}{Goleta, CA}{}{
  \begin{itemize}
		\item Windows, Mac, and Linux user support expert covering all aspects of end user needs for 30+ companies in Santa Barbara and central California.
		\item Implemented internal documentation system and remote monitoring tools for client networks and infrastructure.
  \end{itemize}
}

\cventry{2015 -- 2017}{Senior IT Support Specialist}{Outside Open, LLC}{Santa Barbara, CA}{}{
  \begin{itemize}
    \item Windows, Mac, and Linux user support expert covering all aspects of end user needs for 30+ companies in Santa Barbara and central California.
    \item Backend server management and configuration in Mac, Linux, and Windows environments. NAS and SAN deployment and management.
    \item VMWare and HyperV server migration, deployment, and management.
    \item Microsoft Office 365 and Google Apps support, migration and implementation.
    \item Deployed and managed several FreePBX phone systems
    \item New client onboarding and system deployment
    \item Cisco Networking equipment setup and maintenance for small to medium businesses
  \end{itemize}
}

  \cventry{2011 -- 2015}{IT Support Specialist}{Brooks Institute}{Santa Barbara, CA}{}{
  \begin{itemize}
    \item Part of a 3 person team providing end user support for Faculty and Staff.
    \item Managed 150 Windows PCs and 200 Mac OS faculty and lab computers.
    \item Casper, BigFix, Microsoft Exchange, Apple Remote Desktop.
    \item Setup and support Linux, Windows, and Mac servers.
    \item Managing Nagios alerting and monitoring
    \item Maintained BackupExec backups and tape archiving.
    \item Cisco Networking equipment setup and maintenance
    \item JAMF / JSS server setup, maintenance, image and software management
  \end{itemize}
}

  \cventry{2010 -- Present}{CEO and Founder}{Santa Barbara Hackerspace, Inc.}{Goleta, CA}{}{
  \begin{itemize}
      \item Managing day to day operations, classes, and events
			\item Grew organization from 7 to 60+ members.
			\item Work with our members to develop and maintain internal network, servers, and custom resources.
			\item Maintain the internal networking
			\item Developed and maintain a camera security system and phone system
  \end{itemize}
}

\section{Technical Experience}
\cvline{\textbf{Technologies}}{Linux, Windows, OSX, FreeBSD, Cisco, Juniper, PFSense, Sonicwall, Palo Alto, Asterisk, Barracuda, Polycom, Altium, Kicad, Eagle, Spice Simulations, SQL, Azure, AWS, Apache, Citrix VM, Hyper V, Xen, KVM, OpenScad}
\cvline{\textbf{Languages}}{ BASH, \cpp , Python, C, Powershell, Asterisk}
\cvline{\textbf{Certificates}}{Apple Certified Associate Mac OS 10.11 \& 10.12}


\section{Personal Projects and Experience}
\cvline{\textbf{Awards}\\ \vspace{4.2mm}\textbf{Projects}}{
  \vspace{-3.5mm}
  \begin{itemize}
    \item First contractor to receive the Core Technology Group Bravo award for spearheading the integration of 400+ Jive Communications employees and computers into LogMeIn
		\item Developed the hardware and software for the open source \href{http://tracksoar.com}{\textcolor{color2}{\textbf{Tracksoar}}} weather balloon tracker, and manage assembly, marketing, sales, and inventory
    \item Built toolkit for automatic configuration and compilation of \href{http://mtbales.com/2017/10/12/setting-up-samba-4-as-an-ad-controller/}{\textcolor{color2}{\textbf{Samba}}} 4 as a open source Active Directory replacement
	\end{itemize}
}

\end{document}


%% end of file `template.tex'.
