
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,letterpaper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

\newcommand\cpp{C\raisebox{0.5ex}{\tiny\textbf{++}}}

 \renewcommand*{\labelitemi}{\strut\textcolor{color1}{\large\rmfamily\textbullet}}
% adjust the page margins
\usepackage[top=.1in, bottom=.1in, left=.6in, right=.6in]{geometry}

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Michael}{Bales}
%\address{726 De La Vina}{Santa Barbara Ca 93101}{}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[fixed]{(951) 660-3380}
\email{mtbales@fastmail.fm}                               % optional, remove / comment the line if not wanted
\homepage{mtbales.com}                         % optional, remove / comment the line if not wanted
\social[github]{http://github.com/slapplebags}                              % optional, remove / comment the line if not wanted

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\vspace{-1mm}
\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
\section{Experience}
\cventry{2018 -- Present}{Associate Network Engineer}{LogMeIn}{Goleta, CA}{}{
  \begin{itemize}
    \item SME for deploying and maintaining worldwide Cisco VPN infrastructure for 30+ offices and 4000+ users
    \item worked with a worldwide team to install, manage, and update 500+ L2/L3 switches, ASAs, Fortinet Firewalls, Palo Alto firewalls, WLCs, and APs to maintain 99.9\% network up-time across the company
    \item Designed, built, and maintain custom python based software platform, used for distributed network device configuration, verification, and deployment. 
    \item Worked with remote technicians to install, upgrade, and repair network equipment and connectivity across the organization
    \item Worked with teams within the organization to deploy servers, software, and new equipment by updating VLANs, OSPF, and BGP routing and redistribution as well as firewall permit lists and ACLs
    \item Provided level 3 networking support to end users and other teams within the company
  \end{itemize}
}

\cventry{2015 -- 2017}{Senior IT Support Specialist}{Outside Open, LLC}{Santa Barbara, CA}{}{
  \begin{itemize}
   \item Windows, Mac, and Linux user support expert covering all aspects of end user needs for 30+ companies in Santa Barbara and central California.
    \item Backend server management and configuration in Mac, Linux, and Windows environments. NAS and SAN deployment and management.
    \item VMWare and HyperV server migration, deployment, and management.
    \item Microsoft Office 365 and Google Apps support, migration and implementation.
    \item Cisco Networking equipment setup and maintenance for small to medium businesses
    \item DFARS compliance and enforcement for Defense Contractor clients
  \end{itemize}
}

  \cventry{2011 -- 2015}{IT Support Specialist}{Brooks Institute}{Santa Barbara, CA}{}{
  \begin{itemize}
    \item Managed 150 Windows PCs and 200 Mac OS faculty and lab computers.
    \item Casper, BigFix, Microsoft Exchange, Apple Remote Desktop.
    \item Setup and support Linux, Windows, and Mac servers.
    \item Cisco Networking equipment setup and maintenance
    \item JAMF / JSS server setup, maintenance, image and software management
  \end{itemize}
}

  \cventry{2010 -- Present}{CEO and Founder}{Santa Barbara Hackerspace, Inc.}{Goleta, CA}{}{
  \begin{itemize}
			\item Founded the 501(c)3 non-profit public benefit organization
			\item Managing day to day operations, classes, and events
			\item Grew organization from 7 to 100+ members.
			\item Work with our members to develop and maintain internal network, servers, and custom resources.
			\item Mange the \$100,000 annual budget 
			\item Developed and maintain a camera security system and phone system
  \end{itemize}
}

\section{Technical Experience}
\cvline{\textbf{Technologies}}{Linux, Windows, OSX, FreeBSD, Cisco, Juniper, PFSense, Sonicwall,  Asterisk, Barracuda, Altium, Kicad, Eagle CAD, Fusion360 CAD/CAM, SQL, Azure, AWS, Apache, Citrix VM, Hyper V, Xen, KVM, Netmiko, Palo Alto, Fortinet}
\cvline{\textbf{Languages}}{ BASH, Powershell, Asterisk, Python, \cpp, C}
\cvline{\textbf{Certificates}}{CCNA: 438144170190HMWN, Cisco Certified Specialist - Enterprise Core: TX9MST3FJ3V1QJW3, Cisco Certified Specialist - Enterprise Advanced Infrastructure Implementation: VQLZ93MHLDB1153R, CCNP Enterprise: RKKY532FBK1QQQ35}


\section{Awards and Personal Projects}
\cvline{\textbf{Awards}\\ \vspace{4.2mm}\textbf{Projects}}{
  \vspace{-3.5mm}
  \begin{itemize}
    \item First contractor to receive the Core Technology Group Bravo award for spearheading the integration of 400+ Jive Communications employees and computers into LogMeIn
		\item Developed the hardware and software for the open source \href{http://tracksoar.com}{\textcolor{color2}{\textbf{Tracksoar}}} weather balloon tracker, and manage assembly, marketing, sales, and inventory. Planned and executed 30+ successful scientific research balloon flights.
    \item Built a toolkit for automatic configuration and compilation of \href{http://mtbales.com/2017/10/12/setting-up-samba-4-as-an-ad-controller/}{\textcolor{color2}{\textbf{Samba}}} 4 as a open source Active Directory replacement.
	\end{itemize}
}

\end{document}


%% end of file `template.tex'.
